Instructions for \confname{} Proceedings

### 2019-05-07 papers/EMNLP2019/data-collection.tex
adds messy dataset creation pre-AMT

Goal of this procedure is the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} have an area of~$20-90\%$ of the whole image area.

Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 
Sampling proceeded in dependence on the overall size of the individual collection seeds: 
up to~$800$ objects per seed: all instances, but at most 500, are collected; more than~$800$ objects per seed: all instances, but at most~$1,000$, are collected.  \textbf{double-check}

>>>>

\paragraph{Collection of instance candidates}
Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} have an area of~$20-90\%$ of the whole image area.

\paragraph{Sampling of instances}
Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 
Sampling proceeded in dependence on the overall size of the individual collection seeds: 
up to~$800$ objects per seed: all instances, but at most 500, are collected; more than~$800$ objects per seed: all instances, but at most~$1,000$, are collected.  \textbf{double-check}
